\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{C Purushotham}
\address{ Plot 12, Gulmohar Park Colony \\ Lingampally, Hyderabad 500019  }
\address{ +91~$\cdot$~90100~$\cdot$~26001 \\ purushotham.c@gmail.com }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Education}
    {\bf IIIT Hyderabad} \hfill {\em June 2009} \\ 
    { B.Tech. in Computer Science \& Engineering } \\
    Overall GPA: 6.89
  \end{rSection}
  
  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Python, C++, Java (Basic)\\
      Databases & MySQL, PostgresSQL \\
      Tools & Jenkins CI, SVN, Vim, GIT, Gerrit, JIRA \\
      Automation & Robot Framework, RIDE, JUnit \\
      Operating Systems & Windows, Ubuntu \\
    \end{tabular}
  \end{rSection}
  
  \begin{rSection}{Experience}
  
    \begin{rSubsection}{ValueLabs, Hyd (Client - BlackBerry)}{April 2014 - Present}{Automation Test Developer}{Hyderabad, IN}
    \item Implementing test cases to measure Key Performance Indicators (KPI) of Personal Identification Management (PIM) applications in Android
    \item Implementing and Maintaining an efficient common test automation Jenkins environment requiring very little and low cost maintenance by making the system scalable, secure, consistency and traceability 
    \item Improved the software promotion process by a factor 80\% by having implemented a “mostly touchless promotion” process, where software promotion testing was performed daily. Costs, and promotion process duration, were reduced significantly.
    \item Implementing solutions to prevent software defects from reaching the main codeline by automating a test suite execution when software changes are submitted for review, a failure in the test suite prevents the code submission
    \item Implemented automated test cases, using Python and Robot Framework, to verify and validate the PIM core REST API interface, Phone, SMS/MMS, Camera applications for BB10 OS.
    \item Having an ownership of Automating applications like Phone, Calendar, ISF in BB10.
    \item Disseminated knowledge to other team members to ensure knowledge is transferred
    \item Executing test cases as planned in a timely manner
    \item Providing recommendations to improve product and process requirements
    \item Practitioner of the Agile (Scrum) development methodology
    \end{rSubsection}
    
    \begin{rSubsection}{ValueLabs, Hyd (Client - KarmicLabs)}{August 2016 - September 2016}{Web Developer}{Hyderabad, IN}
    \item Developing a reporting page for user transactions for KarmicLabs project, a payment solutions company, using Python-Flask.
    \end{rSubsection}
    
    \begin{rSubsection}{ValueLabs, Hyd (Client - SnapFish)}{March 2016 - April 2016}{Python Developer}{Hyderabad, IN}
    \item Understanding the existing software which converts Maxwell EDI to Snapfish EDI. This software analyzes huge data of employee insurance details for converting to different formats.
    \item Automated manual tasks involving large XLS sheets using Python Pandas.
    \end{rSubsection}
    
  
    \begin{rSubsection}{Rockwell Collins, India}{May 2009 - November 2012}{Engineer - Software}{Hyderabad, IN}
    \item Implementing Blackbox Requirement Based Automation Tests in Python by analyzing the requirements.
    \item Peer Review test cases, test procedures and results.
    \item Performing Run for Score, Structural Coverage Analysis, Regression tasks
    \item Writing automation scripts to improve the testing process.
    \item Mentor the new joiners and help them to understand the Avionics Domain required.
    \end{rSubsection}
  
  \end{rSection}
  
\begin{rSection}{Awards \& Recognitions }
    \begin{rSubsection}{}{}{}{}
    \item Outstanding contributor to project award in Rockwell Collins
    \item Monthly Python Programming challenge winner multiple times in BlackBerry.
    \end{rSubsection}
  \end{rSection}  

\end{document}
